---
title: "NBA Data Visualization Final"
author: "Desmond Workman"
date: "5/5/2021"
output: 
  html_document:
      toc: TRUE
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(RColorBrewer)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(readr)
library(janitor)
library(effects)

```
 **NBA Player and Scoring Analytics**

The data was found here:[NBA Shooter Data](https://www.kaggle.com/drgilermo/nba-players-stats)

  In this analysis I am looking at historical data from the National Basketball Association. In this study I will analyzing (1)  How did the 2point shot effect the True Shot percentage or (TS%) of some of the best scorers/shooters off all time. (2) I will additionallly be looking at how important the 2 point shot  was to their individual their TS%.The finding will show which players relied more on shots under the 22 foot range.(NBA 3-point line Finally I will be looking at the age distribution of the players in the league.
  
  The players used for the NBA Shooter data

--**Lebron James**--

--**Stephen Curry**--

--**Kareem Abdul Jabbar**--

--**Larry Bird**--

--**Michael Jordan**--

--**Shaquille O'Neal**--

--**Ray Allen**--

--**Carmelo Anthony**--

--**Klay Thompson**--

--**Devin Booker**--


```{r, message=FALSE, echo=FALSE}

nba_player_data <- read_csv("player_data.csv")

nba_season_stats <- read_csv("Seasons_Stats.csv")



nba_season_stats_tidy <-nba_season_stats %>% 
  select(`Player`,Year,`TS%`,`FG%`,`2P%`,`eFG%`,`3P%`,`FGA`,`3PA`, `FGA`, `2PA`, `Pos`)

  nba_best_shooters <- nba_season_stats_tidy %>% 
  filter(Player == "LeBron James" |
           Player == "Stephen Curry" |
           Player == "Michael Jordan*" |
           Player == "Klay Thompson" |
           Player == "Ray Allen" |
           Player == "Carmelo Anthony" |
           Player == "Larry Bird*" |
           Player == "Devin Booker" |
           Player == "Kareem Abdul-Jabbar*" |
           Player == "Shaquille O'Neal*")
  
  
  

```
```{r}
```
## What effects TS% the most?
The accuracy model shows how much the TS% wase affected by theses variables; FG% 2PA% 2P%, eFG%, FGA and 2PA


```{r, message=FALSE, echo=FALSE}

accuracy_model <- nba_best_shooters %>% 
    lm(formula = `TS%` ~`FG%` + `2P%` + `FGA` + `2PA` )
summary(accuracy_model)
  
  
  
    nba_best_shooters %>% 
    ggplot(aes(x = `2P%`,
               y = `TS%`)) +
    geom_point() +
    geom_smooth(method = "lm")+
      ggtitle("Two Point Shot \n Affecting the True Shot Percentage of the Best Shooters \n in the Nba") +
      ylab("True Shot Percentage of Best Shooters")+
      xlab("Two Point Percentage of the Best Shooters")
  
```{r, message=FALSE, echo= True}
```
## Age Distribution of NBA Players

The following graph displays the distribution of ages for players in the NBA.
```{r,message=FALSE, echo=FALSE}

nba_season_stats %>% 
  ggplot(aes(y = `Age`)) +
  geom_bar(col = "black", fill = "grey") +
  ylab("Age of Players in the NBA") +
  xlab("Distribution Count") +
  ggtitle("Distribution of Players Ages in the NBA")
  
```
```{r,}
```
## Best 2 Point Scoring Position
 This graph shows the best 2 point scoring positions in the NBA since 2000. The graph chart compares the 2 point attempts  with 2 point percentages.
 
```{r,message=FALSE,echo=FALSE}

nba_best_shooters %>% 
  ggplot(aes(x = `2PA`,
             y = `2P%`,
              color = `Pos`,
             shape = `Pos`)) +
   geom_jitter( alpha = .55, size = 2.5) +
  ggtitle("Field Goal Attempts Compared to True Shot Percentage rates") +
   ylab("Two Point Completion Percent") +
   xlab("Two Pointers  Attempted")
   
```


